---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# proptrue

This package contains the function prop_true() which determines the proportion of a value x=1. 
This can be used with numerical values or non-numerical values that can be coerced into numerical values such as true/false data (default settings are that true = 1 ).

<!-- badges: start -->
The "b1" folder contains assignment B1 where the function prop_true was written.
The "b2" folder wraps the prop_true function into an R package.
<!-- badges: end -->





## Installation

``` r
There are no dependencies for this package.
Use this to install the package:
devtools::install_github("stat545ubc-2022/assignment-b1-and-b2-mlbaron1/b2/proptrue")

```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(proptrue)
prop_true(x=c(TRUE,FALSE,TRUE))
prop_true(x=c(1,0,0,0))
prop_true(x=c(1,2,3))         
```
